---
title: "Purr Demo"
author: "Sean Nguyen"
output:
  html_document:
    df_print: paged
    theme: flatly
  html_notebook: default
  pdf_document: default
---

```{r, message=FALSE, warning=FALSE}
# Load libraries
library(tidyverse)
library(broom)
```

```{r, message=FALSE, warning=FALSE}
# Set working directory
setwd("~/Desktop")
# Read in data
data <- read_csv("Dummy_data.csv")

data
```


```{r}
# Make data from wide to long
d1 <- data %>% 
  gather(key, values, 3:29) %>% 
  separate(key, into=c("biorep", "Pokemon", "Time"), sep="_")


d1
```


Change columns factor/numeric
```{r}
d1 <- d1 %>% 
  mutate_at(vars(When:Time), as.factor) %>% 
  mutate_at(vars(values),as.numeric)

```

Summarize data
```{r}
d2 <- d1 %>% 
  group_by(When, FA, Pokemon, Time) %>% 
  summarise( N = length(values),
             mean = mean(values),
             sd = sd(values),
             se = sd/sqrt(N))

d2
```


Graph Squirtle, Day data
```{r}

cbbPalette <- c("grey20", "grey", "white")

d2 %>% 
  filter(When =="Day" & Pokemon =="Squirtle") %>% 
  ggplot (aes(x=FA, y=mean, fill=Time))+
  geom_col(colour="black", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.4, 
                size=0.8, colour="grey20", position=position_dodge(.9))+
  scale_fill_manual(values=cbbPalette)+
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  ylab("Fake Units") + # Y axis label
  xlab("") + # X axis label
  ggtitle("Fake Squirtle_Day Data")

```

Faceting d2 dataframe by Pokemon ------------------------------------------
```{r}

d2 %>% 
  ggplot (aes(x=FA, y=mean, fill=Time))+
  geom_col(colour="black", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.4, 
                size=0.8, colour="grey20", position=position_dodge(.9))+
  scale_fill_manual(values=cbbPalette)+
  scale_y_continuous(expand=c(0,0))+ #set bottom of graph
  ylab("Fake Units") + # Y axis label
  xlab("") + # X axis label
  ggtitle("Fake Pokemon Data")+
  facet_grid(When~Pokemon)
```




# Purrr 

The idea is to use the tidyr and purrr package to 'nest' your data  
You essentially will create a dataframe full of dataframes

```{r}
model <- d1 %>% 
  group_by(When, FA, Pokemon) %>%     
  nest() %>%      # nest by Lipid, FA and strain 
  mutate(Shapiro = map(data, ~shapiro.test(.$values)),    # perform a normality test
           ANOVA = map(data, ~aov(values~Time, data = .)),  # calculate the ANOVA for time values
           Tukey = map(ANOVA, ~TukeyHSD(.)))                # calculate the TukeyHSD post hoc analysis


model
```

Query the first row of the 'data' list-column which contains a nested dataframe
```{r}
model$data[[1]] 
```


To see if we nested the data correctly we can look at values that we think my be significant  
Such as Squirtle, Day, 16:1 which corresponds to the 23rd entry in the 'model' dataframe

```{r}
model$data[[23]] # Looking at time values for Squirtle, Day , 16:1 

model$Shapiro[[23]] # Shapiro

model$ANOVA[[23]] # ANOVA

model$Tukey[[23]] # Tukey
```

#  Extracting the data 

We can unnest the results from the Shapiro test

```{r}
Shapiro_df <- model %>%
  unnest(map(Shapiro, tidy)) %>%
  rename(shapiro.statistic = statistic,  # rename the shapiro statistic
         shaprio.p.value = p.value) %>%  # rename the shaprio p value 
  filter(shaprio.p.value >.05)           # Filter on values >0.05, therefore normally distributed

Shapiro_df
```



We can unnest the dataframe to get the ANOVA values 

```{r}
ANOVA_df <- Shapiro_df %>%
  unnest(map(ANOVA, glance)) %>% 
  rename(ANOVA.statistic = statistic)

ANOVA_df
```


We can unnest the dataframe to get the TukeyHSD values

```{r}
TukeyHSD_df <- ANOVA_df %>%
  unnest(map(Tukey, tidy))

TukeyHSD_df
```



Observe for significant differences with p < 0.05

```{r}
Significant <- TukeyHSD_df %>% 
  filter(adj.p.value < 0.05) %>% 
  arrange(adj.p.value)

Significant

Significant %>% 
  select(When:Pokemon, term, comparison, adj.p.value) # Removing the other columns to get the comparisons that you care about
```


